Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
Added four program examples

\subsection{Worlds}
\todo[inline]{Find a good place to describe monotonicity of
  interpretation function.}
\begin{figure}[htbp]
  \centering
  \includegraphics{w11}
  \caption{Relation between local and global capabilities and temporary and permanent regions.}
  \label{fig:cap-world}
\end{figure}
A world is a finite map from region names, modelled as natural numbers, to regions.
We have three types of regions: \emph{permanent}, \emph{temporary}, and \emph{revoked}.
%$\perma$, $\temp$, and $\revoked$. The
%$\perma$ and $\temp$ 
Each permanent and temporary region contains a state transition system, with
public and private transitions, which describes the protocol governing
the evolution of the memory described by the region, similarly to what
has been used in logical relations for high-level
languages~\cite{Ahmed:popl09,Dreyer:jfp12,Devriese:2016ObjCap}. 
The protocols imposed on memory by permanent regions stay in place
indefinitely. This means that any capability, local or global, can
depend on these protocols. The protocols imposed on memory by temporary
regions can be revoked at certain points during execution,
corresponding to the points when local capabilities can be
revoked. This means that local capabilities safely can depend on the
protocols imposed on memory by temporary regions, whereas global
capabilities cannot, since a global capability may stay around
throughout the execution of a program, but a temporary region may be
revoked.
\todo[inline]{Insert reference to figure.}

@@

\caption{Permission-based conditions}
\label{fig:perm-conds}
\end{figure}
\clearpage
}
%subsection introduction
The logical relation defines semantically what it means to be
capability safe. In large parts, capability safety is defined by
when a capability safely can be given to an untrusted piece of
code. In the following paragraphs, we will go through the definitions
of the logical relation and provide an intuition why they define
capability safety.
The definition of the logical relation is found in
\figurename~\ref{fig:logrel}, \figurename~\ref{fig:standard-regions},
and \figurename~\ref{fig:perm-conds}.

@@

\section{Examples}
\begin{itemize}
\item Ticket dispenser
\item The awkward example and variants
\item A sandboxing example?

>>>>

\subsection{Worlds}
\todo[inline]{Find a good place to describe monotonicity of
  interpretation function.}
\begin{figure}[htbp]
  \centering
  \includegraphics{w11}
  \caption{Relation between local and global capabilities and temporary and permanent regions.}
  \label{fig:cap-world}
\end{figure}
A world is a finite map from region names, modelled as natural numbers, to regions.
We have three types of regions: \emph{permanent}, \emph{temporary}, and \emph{revoked}.
%$\perma$, $\temp$, and $\revoked$. The
%$\perma$ and $\temp$ 
Each permanent and temporary region contains a state transition system, with
public and private transitions, which describes the protocol governing
the evolution of the memory described by the region, similarly to what
has been used in logical relations for high-level
languages~\cite{Ahmed:popl09,Dreyer:jfp12,Devriese:2016ObjCap}. 
The protocols imposed on memory by permanent regions stay in place
indefinitely. This means that any capability, local or global, can
depend on these protocols. The protocols imposed on memory by temporary
regions can be revoked at certain points during execution,
corresponding to the points when local capabilities can be
revoked. This means that local capabilities safely can depend on the
protocols imposed on memory by temporary regions, whereas global
capabilities cannot, since a global capability may stay around
throughout the execution of a program, but a temporary region may be
revoked. This is illustrated in \figurename~\ref{fig:cap-world}.

@@

\caption{Permission-based conditions}
\label{fig:perm-conds}
\end{figure}
\clearpage
}
%subsection introduction
The logical relation defines semantically what it means to be
capability safe. In large parts, capability safety is defined by
when a capability safely can be given to an untrusted piece of
code. In the following paragraphs, we will go through the definitions
of the logical relation and provide an intuition why they define
capability safety.
The definition of the logical relation is found in
\figurename~\ref{fig:logrel}, \figurename~\ref{fig:standard-regions},
and \figurename~\ref{fig:perm-conds}. Some definitions are omitted and
explained when needed. The precise definitions can be found in the
technical report.\todo[inline]{add reference to technical report}

@@

\section{Examples}
\begin{figure}[htbp]
  \centering
\begin{lstlisting}
f1: malloc $r_l$ 1
    store $r_l$ 1
    fetch $r_1$ $\adv$
    call $r_1$($[]$,$[r_l]$)
    assert $r_l$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a calling convention not relyant
    on the stack}
  \label{fig:prog-f1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f2: push 1
    fetch $r_1$ $r_\adv$
    scall $r_1$($[]$,$[]$)
    pop $r_1$
    assert $r_1$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a stack-based calling convention.}
  \label{fig:prog-f2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f3: push 1
    fetch $r_1$ $\adv$
    scall $r_1$($[]$,$[r_1]$)
    pop $r_2$
    assert $r_2$ 1
    push 2
    scall $r_1$($[]$,$[]$)
    halt
\end{lstlisting}
  \caption{Simple program that relies on control-flow integrity.}
  \label{fig:prog-f3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
g1:  malloc $r_2$ 1
     store $r_2$ 0
     move $\pcreg$ $r_3$
     lea $r_3$ $\var{offset}$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
     jmp $r_0$
f4:  reqglob $r_1$
     prepstack $r_\stk$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1,r_{\var{env}}]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     load $r_1$ x
     assert $r_1$ 1
     mclear $r_\stk$
     rclear $\RegName \setminus \{r_0,\pcreg\}$
     jmp $r_0$
\end{lstlisting}
  \caption{A program that relies on well-bracketedness of
    \texttt{scall}s to function correctly. $\var{offset}$ is the
    offset to $f4$.}
  \label{fig:prog-g1}
\end{figure}

\begin{itemize}
\item Ticket dispenser
\item The awkward example and variants
\item A sandboxing example?
